Seminarium TI 3700\\ Data Analysis on Twitter(working title)

### 2014-03-19 authorinstr_2.tex
Uitbreiding usermodel
Meer dingen aangepast

\subsection{User Classification}
User classification is the problem of classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted. In this chapter we will discuss User Models, some features used to classify users and some use-cases. 
\subsubsection{User Models}
Before it is possible to classify a user, it is useful to create a model of a user. In their paper F. Abel et al compare the following three ways to model a user \cite{usermodel}:
\begin{itemize}
\item Hashtag-based
\item Entity-based
\item Topic-based

\end{itemize}
After all these approaches are used on the same dataset it appears that the variety of entity-based profiles was much higher than the hashtag based approach. \cite{usermodel} Furthermore the hashtag-based approach fails to create a profile for 5.5\% of the users where the other approaches don't have this problem.  
%TODO uitbreiden

@@

This model is restricted in a way because its output is a set of matrices that illustrates a special case of the Tucker decomposition of a tensor. The tensor is not directly linked to the dataset, but rather implies a ranking. It is therefor only useful in the case of tag-based resource recommendation, and not for resource recommendations with other requirements.

>>>>

\subsection{User Classification}
User classification is the problem of classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted. In this chapter we will discuss User Models, some features used to classify users and some use-cases. 
\subsubsection{User Models}
Before it is possible to classify a user, it is useful to create a model of a user. A user model can vary in three ways. It can vary in the type of profile, the data sources used to enrich the profiles and some temporal constraints. A user profile can be represented by $P(u) = \{(c, w(u,c))| c \in C, u \in U\}$. In this formula $u$ is a user in the set of user $U$ and $c$ is a concept in the set of concepts $C$ is a concept In their paper F. Abel et al compare the following three ways to create a user Profile \cite{usermodel}:
\begin{itemize}
\item Hashtag-based
\item Entity-based
\item Topic-based
\end{itemize}
After all these approaches are used on the same dataset it appears that the variety of entity-based profiles was much higher than the hashtag based approach. \cite{usermodel} Furthermore the hashtag-based approach fails to create a profile for 5.5\% of the users where the other approaches don't have this problem.

@@

This model is restricted in a way because its output is a set of matrices that illustrates a special case of the Tucker decomposition of a tensor. The tensor is not directly linked to the dataset, but rather implies a ranking. It is therefore only useful in the case of tag-based resource recommendation, and not for resource recommendations with other requirements.
